PK object batch mode trial

### 2023-06-15 data-raw/batchMode_trial_gpm.Rmd
Added functionality for calculating rolling AUC

const_pars <- subset(my_pk$prefit$par_DF,
       optimize_param %in% FALSE &
         use_param %in% TRUE) %>% dplyr::select(model, Chemical, Species,
                                         param_name, start) 
const_pars <- const_pars %>%
  pivot_wider(names_from = param_name,
              values_from = start)

my_fit_test <- my_pk$fit %>% unnest(cols = fit) %>%
  group_by(model, method, Chemical, Species) %>%
  dplyr::select(starts_with("sigma_"),
                any_of(sapply(my_pk$stat_model, `[[`, "params") %>%
                         unlist() %>%
                         unique())) # need Rblood2plasma

left_join(my_fit_test, const_pars)

@@

```{r predict_method_remake}
pred_results <- predict(my_pk) # Error about missing parameters

my_test_data <- my_pk$data

my_test_data %>%
  group_by(!!!my_pk$data_group) %>%
  dplyr::select(all_of(c("Time", "Time.Units", "Dose", "Route", "Media"))) %>%
  dplyr::left_join(my_coefs,
            relationship = "many-to-many") -> joined_test_data

# Testing not complete
joined_test_data %>%
  relocate(method, .before = model) %>%
  group_by(across(Chemical:model)) %>%
  nest(.key = "coefs") %>%
  rowwise() %>%
  dplyr::mutate(model_fun = my_pk$stat_model[[model]]$conc_fun,
                predicted_Value = do.call(model_fun,
                                          args = list(
                                            params = coefs,
                                            dose = Dose,
                                            time = Time,
                                            route = Route,
                                            medium = Media
                                          )),
  .after = model) %>%
  head()

my_predict <- function(obj,
                       newdata = NULL,
                       model = NULL,
                       method = NULL,
                       type = "conc",
                       exclude = TRUE,
                       use_scale_conc = FALSE,
                       ...){

@@

  newdata <- newdata %>%
    dplyr::group_by(Route, Media,
                    .add = TRUE) %>%
    mutate(model_fun = obj$stat_model[[model]]$conc_fun) %>%
    reframe(predictions = 
              map(observations,
                  .f = \(x) {
                    x %>%
                      group_by(Time_trans) %>%
                      mutate(Conc_est = sapply(coefs_vector,
                                               FUN = model_fun,
                                               time = Time_trans,
                                               dose = ifelse(obj$scales$conc$dose_norm,
                                                             1, Dose),
                                               route = Route,
                                               medium = Media,
                                               simplify = TRUE,
                                               USE.NAMES = TRUE))
                              })) %>%
    unnest(predictions)

@@

my_pred <- my_predict(my_pk, use_scale_conc = TRUE)

@@

>>>>

@@

```{r predict_method_remake}
my_predict <- function(obj,
                       newdata = NULL,
                       model = NULL,
                       method = NULL,
                       type = "conc",
                       exclude = TRUE,
                       use_scale_conc = FALSE,
                       ...){

@@

  newdata <- newdata %>%
    dplyr::group_by(Route, Media,
                    .add = TRUE) %>%
    mutate(model_fun = case_when(
      type == "conc" ~obj$stat_model[[model]]$conc_fun,
      type == "auc"  ~obj$stat_model[[model]]$auc_fun,
      .default = obj$stat_model[[model]]$conc_fun)) %>%
    reframe(predictions = 
              map(observations,
                  .f = \(x) {
                    x %>%
                      group_by(Time_trans) %>%
                      mutate(Estimate = sapply(coefs_vector,
                                               FUN = model_fun,
                                               time = Time_trans,
                                               dose = ifelse(obj$scales$conc$dose_norm,
                                                             1, Dose),
                                               route = Route,
                                               medium = Media,
                                               simplify = TRUE,
                                               USE.NAMES = TRUE))
                              })) %>%
    unnest(predictions)

  if (type == "conc") newdata <- rename(newdata, Conc_est = "Estimate")
  if (type == "auc") newdata <- rename(newdata, AUC_est = "Estimate")

@@

my_pred <- my_predict(my_pk, type = "auc", use_scale_conc = TRUE)

@@

```{r after_method_update}
# Changed pk_methods coef() and predict() to those above
# Ran the following after making the pk object:
devtools::load_all()

my_coefs_update <- coef(my_pk)
my_pred_update <- predict(my_pk, type = "auc",
                          use_scale_conc = TRUE)

my_pred_update %>%
  filter(model == "model_flat",
         Route == "oral",
         Species == "rat", # hamster has a Fgutabs of zero
         method == "L-BFGS-B") %>%
  View("predicted_update")

my_coefs_update %>%
  filter(model == "model_flat",
         Species == "rat",
         method == "L-BFGS-B") %>%
  View("coef_update")

# Seems to have worked!
```
